% !Mode:: "TeX:UTF-8"

\addcontentsline{toc}{chapter}{附录A  攻读学位期间所发表的学术论文}
\chapter*{附录A~~~~攻读学位期间所发表的学术论文}
\setlength{\parindent}{0em}
\begin{publist}
	
\ifthenelse{\isundefined{\review}}{
	\item \textbf{Haidong Wang}, Zhiyong Li, Jin Yuan, et al. BTN: Neuroanatomical Aligning between Visual Object Tracking in Deep Neural Network and Smooth Pursuit in Brain. Neurocomputing. 2022, 486: 16-26（对应于第二章）
	\item \textbf{Haidong Wang}, Saizhou Wang, Jingyi Lv, et al. Non-local attention association scheme for online multi-object tracking. Image and Vision Computing. 102, 2020: 103983.（对应于第三章）
	\item \textbf{Haidong Wang}, Zhiyong Li, Yaping Li, et al. STURE: Spatial-Temporal Mutual Representation Learning for Robust Data Association in Online Multi-Object Tracking. Computer Vision and Image Understanding. 2022: 103433.（对应于第四章）
	\item \textbf{Haidong Wang}, Xuan He, Zhiyong Li, et al. JDAN: Joint Detection and Association Network for Real-Time Online Multi-Object Tracking. ACM Transactions on Multimedia Computing Communications and Applications. 2022.（对应于第五章）
} {
	\item ACM Transactions on Multimedia Computing Communications and Applications（对应于第五章，第一作者）
	\item Neurocomputing（对应于第二章，第一作者）
	\item Computer Vision and Image Understanding（对应于第四章，第一作者）
	\item Image and Vision Computing（对应于第三章，第一作者）
	
}



%\item Guiji Li, Manman Peng, \textbf{Ke Nai}, et al. Multi-view correlation tracking with adaptive memory-improved update model. Neural Computing and Applications (2019).  https://doi.org/10.1007/s00521-019-04413-4. (SCI 二区)
%\item Jia Zhang, Zhiyong Li, \textbf{Ke Nai}, et al. DELR: A double-level ensemble learning method for unsupervised anomaly detection. Knowledge-Based Systems, 181(2019): 104783. (SCI 二区)
%\item Guiji Li, Manman Peng, \textbf{Ke Nai}, et al. Visual tracking via context-aware local sparse appearance model. Journal of Visual Communication and Image Representation, 2019, 56: 92-105. (SCI 三区)
%\item Song Gao, Zhiyong Li, \textbf{Ke Nai}. Robust object tracking based on adaptive templates matching via the fusion of multiple features. Journal of Visual Communication and Image Representation, 2017, 44: 1-20. (SCI 三区)
%\item Ximing Xiang, Zhiyong Li, \textbf{Ke Nai}. A spatial-aware tracker. ICIP2019. (CCF C类会议)

\end{publist}

