

\documentclass[11pt,journal,onecolumn,draft]{IEEEtran}


% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage[TABBOTCAP]{subfigure}
\usepackage{bm}
\usepackage{upgreek} 
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{color}
\usepackage{cite}
\usepackage[none]{hyphenat}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{caption2}
\usepackage{setspace}

\begin{document}

\begin{center}
	\textbf{\LARGE Cover Letter} 
\end{center}
\vspace{8pt} 
Dear Editor and Reviewers:

\hspace{1em} We want to thank you and the review team for the detailed comments on our submission, and for the opportunity to revise and reconsider the paper to Computer Vision and Image Understanding.  
No conflict of interest exits in the submission of this manuscript, and manuscript is approved by all authors for publication.  
I would like to declare on behalf of my co-authors that the work described was original research. 
All the authors listed have approved the manuscript that is enclosed. 

In this work, we has some contributions.
First, we propose a superior spatial-temporal mutual reinforcement learning (STURE) architecture to solve the problem of feature difference between the spatial features of current detection and the spatial-temporal features of historical sequence for object association.
Second, in order to enhance the mutual learning and identification ability of the proposed method, we have designed three loss functions: cross loss, modality loss and similarity loss, which will help the detection learning network obtain the temporal features.
In addition, a tracking-by-prediction MOT tracking paradigm is designed to alleviate the drift problem of single object tracking by using the reinforced features with STURE, which will improve the accuracy and robustness of the proposed method. 
Therefore, we hope our manuscript can be considered for publication. 

\hspace{1em} We deeply appreciate your consideration of our manuscript.
%and we look forward to receiving comments from the reviewers. 
If you have any queries, please don’t hesitate to contact me at the address below.

\hspace{1em} Thank you and best regards.

\hspace{1em} Yours sincerely,

\hspace{1em} Zhiyong Li
\vspace{20pt} 

Corresponding author:

Name: Zhiyong Li 

E-mail: zhiyong.li@hnu.edu.cn 

\end{document}


